A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-27 dl-paper.tex
Minor fix

\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem for the unstable even-dimensional orthogonal Steinberg groups.
$\mathbb{P}^1$-glueing theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
 positive solution of which currently is only known in the case of linear Steinberg groups. \end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

\begin{rem} It is possible to give a different proof of the above lemma in the case $\Phi = \rC_\ell$ for $\ell \geq 5$ under the additional assumption that the characteristic of $k$ is not $2$. Indeed, we have the following chain of isomorphisms:
\[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. Thus, we see that the result of Morita and Rehmann agrees with the modern literature on higher Grothendieck--Witt groups. \end{rem}

>>>>

\begin{abstract} We prove a $\mathbb{P}^1$-glueing theorem (also called Horrocks theorem) for the unstable even-dimensional orthogonal Steinberg groups.
Horrocks theorem for Steinberg groups is one of the key ingredients needed for the proof of the $\K_2$-analogue of Serre's problem, 
 positive solution of which currently is only known in the linear case. \end{abstract}
\maketitle
\section{Introduction}
Recall that the classical Serre problem on projective modules asks if any projective module over a polynomial ring $R = k[x_1,\ldots, x_n]$ over a field $k$ is free. This problem was positively settled by D.~Quillen~\cite{Qu76} and A.~Suslin~\cite{Su76}, and its solution played an important role in the development of algebraic K-theory. We also refer the reader to the textbook~\cite{Lam10} for a comprehensive account on the problem, its history and the subsequent solution.

@@

\begin{rem} It is possible to give a different proof of the above lemma in the case $\Phi = \rC_\ell$ for $\ell \geq 5$ under the additional assumption that the characteristic of $k$ is not $2$. Indeed, we have the following chain of isomorphisms:
\[ \K_2(C_\infty, k[X, X^{-1}]) \cong \GW_2^2(k[X,X^{-1}]) \cong \GW_2^2(k) \oplus \GW_1^1(k) \cong \K_2^\mathrm{MW}(k) \oplus \K_1^\mathrm{MW}(k),\]
in which the first two isomorphisms are obtained from~\eqref{GW-concrete} and~\cref{bass-ft} and the last one follows from the isomorphism $\GW_1^1(k) \cong \K_1^\mathrm{MW}(k)$ of~\cite[Lemma~4.1.1]{AF17} and Matsumoto's theorem.
It remains to invoke the stability theorem~\cite[Theorem~9.4]{Pa89} to obtain the assertion in the unstable case. \end{rem}
